Rapid Epidemiological Analysis of Comorbidities and Treatments as risk factors for COVID-19 in Scotland (REACT-SCOT): a population-based case-control study

### 2020-07-28 casecontrol.Rmd
updated pharmacoepi manuscript

For each case, the CHI database was used to select up to ten controls matched for sex, one-year age band and registered with the same primary care practice, who were alive and resident in Scotland on the day as the first date that the case tested positive.  For fatal cases who had not tested positive, the incident date was assigned as 14 days before death.  To ensure that cases and controls were representative of the same population at risk, the 0.6% of cases who were recorded on the CHI database as no longer alive and resident in Scotland on the day that ECOSS recorded them as testing positive were also excluded.  As this is an incidence density sampling design, it is possible and correct for an individual to appear in the dataset more than once, initially as a control and subsequently as a case.  
For this analysis based on ascertainment of positive test results up to `r gsub("^0", "", format(max(cc.severe$SPECDATE, na.rm=TRUE), "%d %B %Y"))`, entry to critical care up to `r gsub("^0", "", format(maxdate.sicsag, "%d %B %Y"))` and deaths registered up to `r format(max(cc.severe$DATE_OF_REGISTRATION, na.rm=TRUE), "%d %B %Y")` there were `r nrow(cc.severe[CASE==1])` cases and `r nrow(cc.severe[CASE==0])` controls.  Among fatal cases, `r percent.withindays[6]`% of deaths were registered within 5 days.

>>>>

For each case, the CHI database was used to select up to ten controls matched for sex, one-year age band and registered with the same primary care practice, who were alive and resident in Scotland on the day as the first date that the case tested positive.  For fatal cases who had not tested positive, the incident date was assigned as 14 days before death.  To ensure that cases and controls were representative of the same population at risk, the 0.6% of cases who were recorded on the CHI database as no longer alive and resident in Scotland on the day that ECOSS recorded them as testing positive were also excluded.  As this is an incidence density sampling design, it is possible and correct for an individual to appear in the dataset more than once, initially as a control and subsequently as a case.  
For this analysis based on ascertainment of positive test results up to `r gsub("^0", "", format(max(cc.severe$SPECIMENDATE, na.rm=TRUE), "%d %B %Y"))`, entry to critical care up to `r gsub("^0", "", format(maxdate.sicsag, "%d %B %Y"))` and deaths registered up to `r format(max(cc.severe$DATE_OF_REGISTRATION, na.rm=TRUE), "%d %B %Y")` there were `r nrow(cc.severe[CASE==1])` cases and `r nrow(cc.severe[CASE==0])` controls.  Among fatal cases, `r percent.withindays[6]`% of deaths were registered within 5 days.
